Predictive 3D modelling of free oblique cutting of Ti6Al4V titanium alloy and experimental validation for a wide range of conditions\\ \FD{Include AI?}

### 2022-09-17 Article.tex
Update of fig. temporal evolution of forces

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}\FD{Style of legend different than text}
\label{ExpNum_Forces_v10_40µ_6}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{Figures/ExpNum_Forces_v10_40µ_6}
\caption{Temporal evolutions of experimental (E) and numerical (N) forces at 6°, 10 m/min and 40 \textmu{}m: dispersion around mean experimental values and linear extrapolation of numerical values in dashed}
\label{ExpNum_Forces_v10_40µ_6}
\end{figure}
